---
title: "LAB1"
author: Шаршов Иван
format: 
    md:
        output-file: README.md
engine: knitr
---

# №1

# In this lesson, we will explore some basic building blocks of the R programming language.

```{r echo=TRUE}
5+7
```

```{r echo=TRUE}
x <- 5+7
x
x-3
y <- x-3
y

z <- c(1.1, 9, 3.14)
z
c(z, 555, z)
z*2+100

my_sqrt <- sqrt(z-1)
my_sqrt

my_div <- z/my_sqrt
my_div

c(1,2,3,4)+c(0,10)

z * 2 +1000

my_div
```
# №2
# In this lesson, you'll learn how to examine your local workspace in R and begin to explore the relationship between your workspace and the file system of your machine.
```{r}
getwd()
ls()
x <- 9
list.files()

?list.files

args(list.files)

old.dir <- getwd()

dir.create("testdir")

setwd("testdir")

file.create("mytest.R")
list.files()

file.exists("mytest.R")

file.info("mytest.R")

file.rename("mytest.R","mytest2.R")

file.path("mytest3.R")

file.path("folder1", "folder2")

dir.create(file.path("testdir2","testdir3"),recursive = TRUE)

setwd(old.dir)
```
# №3
# In this lesson, you'll learn how to create sequences of numbers in R.

```{r}
1:20

pi : 10

15:1

seq(1, 20)
seq(0,10, by=0.5)
seq(5,10, length=30)
my_seq <- seq(5,10, length=30)
length(my_seq)
1:length(my_seq)
seq(along.with = my_seq)
seq_along(my_seq)
rep(0, times=40)
rep(c(0,1,2), times=10)
rep(c(0,1,2), each=10)
```
# №4
# The simplest and most common data structure in R is the vector.
```{r}
num_vect <- c(0.5,55,-10,6)
tf <- num_vect < 1
tf
num_vect >= 6
my_char <- c("My","name", "is")
my_char
paste(my_char, collapse = " ")
my_name <- c(my_char, "Ivan")
my_name
paste(my_name,collapse = " ")
paste("Hello", "world!", sep = " ")
paste(1:3, c("X", "Y", "Z"), sep = "")
paste(LETTERS, 1:4, sep = "-")

```
# THE END

